\documentclass[class=report,11pt,crop=false]{standalone}
\input{../Style/ChapterStyle.tex}
\begin{document}

\chapter*{Acknowledgements}
First, I want to express my gratitude to my supervisor, Dr. Yunus, who has consistently provided invaluable guidance and wisdom over the past few months. I appreciate your unwavering willingness to assist me, engage in meaningful discussions, and consistently go the extra mile to support me. Having you as a mentor has made this journey exceptionally fulfilling, and I am thankful for the knowledge and insights you've imparted. Your humility and kindness will continue to inspire me.

I would like to extend my appreciation to the Council for Scientific and Industrial Research (CSIR) for generously providing the measured data that were critical in this project's development.

To all of my friends, thank you for your love and support and your part in my journey. Ryan, thank you for believing in me when I failed and encouraging me when I felt defeated. Mishay, thank you for always being the voice of reason and rational thinking when everything felt overwhelming to me. Shams, your companionship throughout the last few years has provided me with many necessary moments of silliness and comfort. And to Justin Pead, thank you for being my mentor, for helping me solve many problems and providing me with endless oversized cups of tea to drown my stress in.

And, to my mom, who has been my biggest fan throughout my entire life. It's challenging to put into words just how much I value the sacrifices you've made and the support you've provided. The best I can offer is a heartfelt thank you, repeated over infinity times infinity.
\end{document}