% ----------------------------------------------------
% Recommendations
% ----------------------------------------------------
\documentclass[class=report,11pt,crop=false]{standalone}
\input{../Style/ChapterStyle.tex}
\input{../FrontMatter/Abbreviations.tex}
\begin{document}
% ----------------------------------------------------
\chapter{Recommendations \label{ch:recommendations}}
% ----------------------------------------------------
The time constraints of this project have prevented a holistic investigation into the work discussed in this report. Recommendations for future work on this project are briefly summarised in this chapter.

\section{Algorithms}
\begin{itemize}
    \item Other low computation \gls{tmc} algorithms should be investigated and tested.
    \item The effect of the \gls{cpi} on algorithm performance should be investigated. In this report, the value was kept constant.
    \item Low computation \gls{rmc} algorithms should be investigated to improve the images produced, whilst still meeting the timing requirements.
    \item Use a wider variety of data to test algorithm performance to ensure a more robust \gls{qlp}.
\end{itemize}
\section{Quick-look Processor}
\begin{itemize}
    \item Investigate the processor's performance on other datasets of objects other than sea vessels to determine if it can be used in other applications.
    \item Improve the processor's robustness by facilitating the use of other \gls{isar} data types, not only \gls{sfw}.
    \item The developed \textsc{MATLAB} code should be implemented in a non-licensed programming language like C++ to increase accessibility and possibly performance.
    \item Improve the functionality of the \gls{qlp} app by adding additional features and error handling.
\end{itemize}


% ----------------------------------------------------
\ifstandalone
\bibliography{../Bibliography/References.bib}
\printnoidxglossary[type=\acronymtype,nonumberlist]
\fi
\end{document}
% ----------------------------------------------------